\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-28 paper/algorithm.tex

To motivate the restriction of imputation types, we consider the implications of allowing arbitrary imputations.
If we allow any arbitrary subset of attributes to be imputed, then we would need to consider $O(2^{|D|+1})$ different imputation operators before each relational operator.
This would increase the overall complexity of the algorithm drastically.

>>>>

To motivate the restriction of imputation types, we consider the implications of allowing arbitrary imputations.
If we allow any arbitrary subset of attributes to be imputed, then we would need to consider $O(2^{|D|+1})$ different imputation operators before each relational operator where $D$ is the set of dirty attributes in all tables.
This would increase the overall complexity of the algorithm drastically.
